Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-11-01 batchdedup/scheduling.tex
update coe analysis

\section{Round Scheduling}
\label{sect:scheduling}
The simplest way to take advantage of the efficiency of batch processing is to
schedule all the work to be done in one round.  This works well if all of the
data being backed up are only copies, e.g. a separate backup system which data
is sent to over the network. However, in our case we are backing up the
original virtual disk, so a single round backup presents several problems.
The first is that the average turnaround time for a VM is the time it takes to
backup all the VMs. The second, which is related to the first, is that a single
round backup has the highest cost to maintain a consistent view of the virtual
disks. We use Copy on Write (CoW) for this, and the consistent view must be
maintained between stage 1a and stage 2b, which can have sisgnificant cost if
the system must wait for every single VM before unlocking any of the VMs.
Other studies have
shown that as much as 8\% or even more of total capacity must be reserved for
CoW \cite{EMCIncrementalDataChanges}. The actual cost of CoW is a factor of the
data size, the write rate, and duration CoW is taking place. The data size
isn't something we can change, nor the write rate, but we can minimize the
duration that a given VM is undergoing CoW. By minimizing the backup time for
individual VMs we also improve CoW cost. To evaulate our
CoW cost improvement, we assume a poisson distribution of
writes (which closely fits the meaured results from
\cite{EMCIncrementalDataChanges}).

@@

In the above model, $n$ is the number of dirty segments, $t$ is the time under
CoW, $w$ is the
write rate during CoW, $d_1$ is the \% of clean data (which doesn't go under
CoW), and $c$ is a constant determining how likely writes are to touch dirty
segments which haven't yet been copied vs. dirty segments which have already
been copied during the current backup. With this CoW cost model and the earlier
performance model, we can estimate the CoW cost of a given backup schedule.
Note that CoW ends in Stage 2b, so only the time up to the end of 2b counts
towards CoW. \todo{we still need to pick a value for $c$}

>>>>

\section{Round Scheduling}
\label{sect:scheduling}
The naive way to take advantage of the efficiency of batch processing is to
schedule all the work to be done in one round.  
% This works well if all of the
% data being backed up are only copies, e.g. a separate backup system which data
% is sent to over the network. 
However, in our case we are backing up the
live virtual disks, thus such single round backup presents several problems
in our synchronous approach.
This first is that in order to preserve a consistent view of VM images, we apply
Copy-on-Write (CoW) to protect the dirty segments against incoming disk writes during 
the backup period of stage 1 and 2.
Previous studies have shown that as much as 8\% or even more of total capacity must be reserved for
CoW \cite{EMCIncrementalDataChanges}, while the actual cost of CoW is a factor of the
data size, the write rate, and duration of CoW protection.
The second problem is that a single round backup brings the highest cost of CoW
because of the workload in stage 1a is imbalanced,
causing machines with small VMs to wait while CoW protection is turned on.
Thus we must minimize the duration that a given VM is undergoing CoW protection.

% The first is that the average turnaround time for a VM is the time it takes to
% backup all the VMs. The second, which is related to the first, is that a single
% round backup has the highest cost to maintain a consistent view of the virtual
% disks. We use Copy on Write (CoW) for this, and the consistent view must be
% maintained between stage 1a and stage 2b, which can have significant cost if
% the system must wait for every single VM before unlocking any of the VMs.
% Other studies have shown that as much as 8\% or even more of total capacity must be reserved for
% CoW \cite{EMCIncrementalDataChanges}. The actual cost of CoW is a factor of the
% data size, the write rate, and duration CoW is taking place. The data size
% isn't something we can change, nor the write rate, but we can minimize the
% duration that a given VM is undergoing CoW. By minimizing the backup time for
% individual VMs we also improve CoW cost. 
To evaulate our CoW cost, we assume the incoming writes point to random disk locations, 
which would incur a CoW operation over a segment if the write location fall into a dirty segment
for the first time (consequential writes to that segment will be re-directed 
to the new copy so there's no extra cost). Therefore the number of dirty segments needs to be copied represents
the CoW cost of a VM, which follows a poisson distribution (similar results are meaured from \cite{EMCIncrementalDataChanges}).

@@

In the above model, $n$ is the number of dirty segments, $t$ is the time under
CoW protection, $w$ is the
write rate during CoW, $d_1$ is the \% of clean data (which doesn't go under
CoW), and $c$ is a constant determining how likely writes are to touch dirty
segments which haven't yet been copied vs. dirty segments which have already
been copied during the current backup. With this CoW cost model and the earlier
performance model, we can estimate the CoW cost of a given backup schedule.
Note that CoW ends in Stage 2b, so only the time up to the end of 2b counts
towards CoW. \todo{we still need to pick a value for $c$}
